Eurovision Song Contest: semifinal 1, 2009

### 2019-12-23 inst/eurovision.Rmd
typo

```{r,orderplot}
m <- maxp(euro2009)  # likelihoods
points_scored <- rowSums(wiki_matrix,na.rm=TRUE)  # points
ox <- rank(-points_scored)
oy <- rank(-m)
par(pty='s') # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,18),ylim=c(0,18),pch=16,
xlab="official order",ylab="my order",main="Eurovision 2009")
par(xpd=TRUE) # allow country names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(m)[i],pos=4,col='gray') }
par(xpd=FALSE) # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

>>>>

```{r,orderplot}
m <- maxp(euro2009)  # likelihoods
points_scored <- rowSums(wiki_matrix,na.rm=TRUE)  # points
ox <- rank(-points_scored)
oy <- rank(-m)
par(pty='s') # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,18),ylim=c(0,18),pch=16,
xlab="official order",ylab="my order",main="Eurovision 2009")
par(xpd=TRUE) # allow country names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(m)[ox[i]],pos=4,col='gray') }
par(xpd=FALSE) # stop diagonal line from protruding beyond plotting region
abline(0,1)
```
